Embedding to Reference t-SNE Space Addresses Batch Effects in Single-Cell Classification

### 2021-05-13 paper-revision/response-to-reviewers.tex

\answer{We thank the reviewer for this comment. We have restructured the paper.

	We have added a ``Related work'' section, where we describe batch-effects in more detail. We have also moved the description of scMap-Cluster from the ``Experiments'' section to this section. While it is true that these approaches are, in essence, transfer learning, the data sets produced by single-cell RNA-seq are sufficiently different from data sets from other fields of machine learning that they requires specialized methods, which we describe in the ``Related work'' section.
}

\reviewc{r2q3}{The current paper is an extension of a conference paper submitted to the conference Discovery Science 2019. The authors should explicitly provide in the text the actual novel contributions with respect to the conference version.}

\answer{
	We added a paragraph to the end of the introduction explicitly listing our contributions. The differences from the conference version are mainly an improved experimental section, where we show that a naive placement of the data points leads to misleading conclusions, and that optimization produces more reasonable results. Additionally, we provide the classification evaluation where we compare the classification accuracy of our proposed approach and standard machine learning methods for scRNA-seq data.
}

### 2021-05-13 paper-revision/policar2020-tsne-embedding.tex
Add paragraph listing contributions

>>>>

Our contributions are two-fold. 
\begin{enumerate}
  \item We introduce a theoretically-grounded extension of the t-SNE
  visualization algorithm, which allows the embedding of new data points into
  existing, reference visualizations. Our extension is easily incorporated into
  existing approximation schemes, enabling it to be applied to large data sets.
  We show that optimization using the default t-SNE parameters is highly
  unstable and propose parameter values which lead to stable convergence.
  \item We show that our straightforward extension can be used to mitigate batch
  effects in single-cell RNA-seq data.
\end{enumerate}
